Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-05-13 Scripts/Initial_Analysis.Rmd
All ready to re-run proportion analysis in Hall 1000
fied return function fun proportion
updated paths

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE,repos = "http://cran.us.r-project.org")
  sapply(pkg, require, character.only = TRUE)
}

@@

ipak(packages)

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  data_path <- "Z:/DATA/DBEM/"
}
if(Sys.info()[7] == "carmelia"){
  data_path <- paste(here(),"/Temporal_Data/",sep = "")
  DBEM_path <- paste(data_path,"DBEM/",sep="")
  result_path <- paste(here(),"/Temporal_Data/Results/",sep="")
}
if(Sys.info()[7] == "hall1000"){
  data_path <- "/Volumes/DATA/JULIANO_NEYMAR/TransEmergence/Data/"
  DBEM_path <- "/Volumes/DATA/DATA/DBEM/"
  result_path <- "/Volumes/DATA/JULIANO_NEYMAR/TransEmergence/Results/"
}

# standarize maps
ggtheme_map <- function(base_size = 9, Region = "NA") {

  theme(text             = element_text(#family = "Helvetica",
    color = "gray30", size = base_size),
    plot.title       = element_text(size = rel(1.25), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "transparent"),
    strip.background =element_rect(fill = "transparent"),
    strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
    axis.line        = element_blank(), # element_line(colour = "grey30", size = .5))
    axis.ticks       = element_blank(),
    axis.text        = element_blank(),
    axis.title       = element_blank(),
    legend.key       = element_rect(colour = NA, fill = NA, size = 4),
    legend.position = "bottom",
    legend.key.width =unit(5,"line")
  )
}

@@

## Global functions

Here we just run functions that will be used multiple times douring the analysis

### Fun `dbem_import`

This function reads the DBEM data for each year and ensamble (ESM model) from 102 20 111

```{r dbem_import, eval = T, echo = T}

dbem_import <- function(taxon_key, #Except taxon_key 
                        year, #Expects sequence of years 
                        ensamble, #Expects a number of the ensamble
                        data_type, #Expects either "Abd" or "Catch"
                        path = "NA"){

  years <- year_df %>% pull(year)

  D_Path <- paste(path,"mpa0F1ENS",ensamble,"/",taxon_key,"/",taxon_key,data_type,years,".txt",sep="")

  #### Importing data ####
  cur <- lapply(D_Path, FUN=fread, na.strings="NA")

  if(length(cur)>0){
    cur <- cur[sapply(cur, function(d) nrow(d) >= 1)] 
    colnames <- c("index", "value")
    cur <- lapply(cur, setNames, colnames)
    df <- bind_rows(cur, .id = "column_label")
    if(nrow(df)>0){
      frame_key <- tibble(column_label = seq(1,length(unlist(years)),1), 
                          "year"=years) %>% 
        mutate(column_label=as.character(column_label))
      df <- left_join(df, frame_key, by="column_label") %>% select(-column_label)
      df <- df %>% mutate(data_type=data_type,
                          taxon_key = taxon_key,
                          ensamble = ensamble
      )
    }
  } else {
    df <- tibble()
  }
    return(df)
} #Function end

# x <- dbem_import(
#   taxon_key <- 600004,
#   Year <- year_df,
#   data_type <- "Catch",
#   ensamble = 102,
#   # ensamble_list =ensamble,
#   path <- DBEM_path
# )

# attach(x)
# head(x)
# unique(year)
# unique(ensamble_list)
# detach(x)

@@

EEZIDs_List <- read_excel(paste(data_path,"Spatial/V_Lam/Updated_EEZList_17June2016.xlsx",sep="")) %>% 
  clean_names()
EEZ_CellID <- read_excel(paste(data_path,"Spatial/V_Lam/EEZ_CellID.xlsx",sep="")) %>% 
  clean_names()
colnames(EEZ_CellID) <- c("eezid","index")

Lon_Lat_DBEM <- read.csv(paste(data_path,"Spatial/Lon_Lat_DBEM.txt",sep=""), header=FALSE)
colnames(Lon_Lat_DBEM) <- c("index","lon","lat")

index_code <- EEZIDs_List %>% 
  left_join(EEZ_CellID) %>% 
  rename(eez_name = name) %>% 
  left_join(Lon_Lat_DBEM,
            by = "index")

write_csv(index_code,
          "sau_index_code.csv")

@@

@@

```{r EstPropChange, eval = F, echo = F}

@@

```{r Emerging_control_panel, eval = F}

@@

```{r Proportion_routine, eval = F, echo = F}

@@

```{r GetTransIndex, eval = F, echo = T}

@@

```{r Emerging_control_panel, eval = F}

@@

```{r fun_SummaryProp, eval = T, echo =F}

@@

```{r fun_EEZProp, eval = T, echo = F}

@@

```{r fun_PropChange, eval = T, echo =F}

@@

```{r TransIndex, eval = F, echo = T}

>>>>

library(MyFunctions)

@@

my_lib(packages)

@@

@@

EEZIDs_List <- my_path("G", extra_path = "Spatial/DBEM", name="Updated_EEZList_17June2016.xlsx", read = TRUE) %>% 
  clean_names()

EEZ_CellID <- my_path("G", extra_path = "Spatial/DBEM", name="EEZ_CellID.xlsx", read = TRUE) %>% 
  clean_names()

colnames(EEZ_CellID) <- c("eezid","index")

Lon_Lat_DBEM <- my_path("G", extra_path = "Spatial/DBEM", name="Lon_Lat_DBEM.txt", read = TRUE, header = FALSE)
colnames(Lon_Lat_DBEM) <- c("index","lon","lat")

Index_Code <- EEZIDs_List %>% 
  left_join(EEZ_CellID) %>% 
  rename(eez_name = name) %>% 
  left_join(Lon_Lat_DBEM,
            by = "index")

# Save Index data for future 
write_csv(index_code,
          paste(my_path("G",extra_path = "Spatial/DBEM"),"sau_index_code.csv",sep="")
          )

@@

# The path
Path_SAU <- my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile")

# The File
File_Name <- "SAUEEZ_July2015.shp"

# Load it!
SAU_eez_sf <- st_read(dsn = Path_SAU,
                        layer =file_path_sans_ext(File_Name)
                      ) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1)

@@

```{r EstPropChange, eval = T, echo = F}

@@

```{r Emerging_control_panel, eval = T, echo = F}

@@

```{r Proportion_routine, eval = T, echo = F}

@@

```{r GetTransIndex, eval = T, echo = T}

@@

```{r Emerging_control_panel, eval = T, echo = T}

@@

```{r fun_SummaryProp, eval = F, echo =F}

@@

```{r fun_EEZProp, eval = F, echo = F}

@@

```{r fun_PropChange, eval = F, echo =F}

@@

```{r TransIndex, eval = F, echo = F}
